---
title: "Data Visualization Gallery"
date: "November 2022"
output: 
  html_document:
    toc: true
    toc_float: true
---


> *This is a collection of static data visualizations.*


```{r setup, include=FALSE}

knitr::opts_chunk$set(eval=TRUE, include=FALSE, echo=FALSE, comment=NA, cache=FALSE)

```

```{r load-packages}

library(fontawesome)
library(tidyverse)
library(openxlsx)
library(mapview)
library(here)
library(sf)

path <- here()

```

# Hexbin Map {.tabset}

## Map

```{r make-map}



```


## `r fa( "info-circle", fill = "#3E6E82" )`

- This visualization is a hexbin map of the United States; it features data from the Centers for Medicare and Medicaid Services' Multiple Chronic Conditions (MCC) [dataset](https://data.cms.gov/medicare-chronic-conditions/multiple-chronic-conditions). 

- The MCC data were retrieved through the Centers for Medicare and Medicaid Services [API](https://data.cms.gov/api-docs). More information about the dataset can be viewed in the [data dictionary](https://data.cms.gov/resources/multiple-chronic-conditions-data-dictionary) and [methodology documentation](https://data.cms.gov/resources/medicare-chronic-conditions-methodology).

- The hexagonal shapefile of the United States was obtained from [Carto](https://team.carto.com/u/andrew/tables/andrew.us_states_hexgrid/public/map). It can be downloaded in other formats, such as GeoJSON.

- Holtz Yan's excellent [hex bin map tutorial](https://r-graph-gallery.com/328-hexbin-map-of-the-usa.html) on The R Graph Gallery provided the data source for the hexagonal shapefile—as well as helpful hints for manipulating the file.

- Thanks to Bruno Kenzo for [inspiration](https://github.com/KenzoBH/Visualizations) on how to display this collection of data visualizations.

- Finishing touches were created with the aid of Holtz Yan's [Pimp my RMD: a few tips for R Markdown](https://holtzy.github.io/Pimp-my-rmd/).

- The color palette was created using Cara Thompson's [monochromeR package](https://github.com/cararthompson/monochromeR).

- The alt text was generated using the formula provided by Liz Hare in her October 2022 [presentation](https://lizharedogs.github.io/RLadiesNYAltText "Click here to be directed to Liz's presentation slides.") for R-Ladies NYC.


# Lollipop Graph


<hr />
<p style="text-align: center;">Created by Toyin L. Ola</p>
<p style="text-align: center;"> <a href="https://github.com/toylyol/misc-data-viz" class="fa-solid fa-code"></a></p>